---
title: Vancomycin Dose Regimen Predicted Using Bayesian Simulation
date: \today
params:
  logo: logo.png
  cover: cover.png
  iblue: 2b4894
  igray: d4dbde
  gender: NULL
  age: NULL
  bayes: NULL
documentclass: article
fontsize: 10
papersize: a4paper
output: 
  IReports::businessReport:
    keep_tex: TRUE
    latex_engine: xelatex
    resetStyleFiles: FALSE
header-includes: 
  - \newcommand{\logo}{`r gsub("_", "\\_", params$logo)`}
  - \newcommand{\cover}{`r gsub("_", "\\_", params$cover)`}
  - \newcommand{\iblue}{`r params$iblue`}
  - \newcommand{\igray}{`r params$igray`}
include-before:
  - \renewcommand{\contentsname}{Table of Contents}
  - \renewcommand{\pagename}{Page}
---



```{r setup, include = FALSE}
# packages
library(dplyr)
library(knitr)
library(xtable)

# settings
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

\maketitle
\tableofcontents
\addcontentsline{toc}{section}{Contents}
\clearpage

\section{Patient's Characteristics}
Gender: `r params$gender` \
\
Age: `r params$age` \
\
Creatinine clearance: `r round(params$bayes$crcl)` mL/min

\section{Model Description}
`r params$bayes$helpText`



\section{Results}

\subsection{Dosing Regimen}
Loading Dose: `r params$bayes$initDose` mg \
\
Maintenance Dose: \

* `r params$bayes$TIME_1`H: `r round(params$bayes$dose2)` mg

* `r params$bayes$TIME_2`H: `r round(params$bayes$dose3)` mg 

* `r params$bayes$TIME_3`H: `r round(params$bayes$dose4)` mg

* `r params$bayes$TIME_4`H: `r round(params$bayes$dose5)` mg 
  

\subsection{Plot}
```{r results = "asis"}
params$bayes$plot_pk
```

\subsection{Table}
```{r results = "asis"}
kable(params$bayes$cleaned_table, format = "latex", longtable = TRUE) %>%
  kable_styling()
```

